PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-15 qfenv_paper/qf_environment.tex
Fixed the Abstract

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{5}, 
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$. We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).

For each of these subsamples, we examine the stellar mass function (SMF) evolution and compute the $f_{\rm{Q}}(\mathcal{M}_{*})$. We find that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range. Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range. These results suggest that the evolution of the quiescent fraction is independent of environment and provide constraints on quenching mechanisms in high density environments such as groups and clusters.  
\end{abstract}

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{5}, 
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).

For quiescent and star-forming galaxies in low or high density environments, we examine the evolution of their stellar mass function (SMF) evolution. Then using the SMFs we compute the $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify the evolution of $f_{\rm{Q}}(\mathcal{M}_{*})$ within our redshift range. We find that in both low and high density environments the quiescent fraction increases with cosmic time. Moreover, we illustrate that galaxy populations in high density environments have significantly higher quiescent fractions than galaxy populations in low density environments. Furthermore, by comparing the quiescent fraction evolutions, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments. These results suggest that quenching due to the environment has a moderate effect on the quiescent fraction evolution and provide constraints on quenching mechanisms in high density environments such as groups and clusters. 
\end{abstract}
